
\documentclass[ignorenonframetext,10pt,aspectratio=169]{beamer}

\usepackage{umut}
\usepackage{umuttr}
\usepackage{usynsem}
\usepackage[utf8]{inputenc}
\usepackage{uling}
\usepackage{natbib,unatbib}
\usepackage{linguex}
         \renewcommand{\refdash}{}
\usepackage{ubeamer}
\usepackage{verbatim}

\usepackage{fancyvrb}

\usepackage{tikz-qtree}
\usetikzlibrary{er,positioning}

\title{Subjects}
\author{\  \\  {\it Partly based on Koeneman \& Zeiljstra (2017)} \\ \vspace{20pt} Umut \"Ozge\\  }

	\date{COGS 532: Theoretical Linguistics\\ METU, Informatics}

\begin{document}

\begin{frame}\frametitle{}
\thispagestyle{empty}
\maketitle
\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\begin{frame}[t,plain]{Extended Projection Principle}
\vspace{50pt}
EPP: Every sentence has a subject.

\end{frame}

\begin{frame}[t,plain]{Passive}


\ex. John killed Bill.

\ex. Bill \alert{was} killed (by John).

\ex. They \alert{were} killed (by John).

\end{frame}

\begin{frame}[t,plain]{The expletive {\it it}}

\ex. It rains/snows.

\end{frame}

\begin{frame}[t,plain]{Back to Passive}

\begin{itemize}

\item Which argument to drop when passivizing?
\item Which argument to ``promote'' to SUBJ?
\pause
\item $\Theta$-hierarchy: AGENT > RECIPIENT > THEME/PATIENT > GOAL
\end{itemize}


\ex.
\a. John gave Mary the book.
\b. Mary was given the book.
\b. *The book was given Mary.

\ex.
\a. John gave the book to Mary.
\b. The book was given to Mary. 
\b. *Mary was given the book to.

\end{frame}

\begin{frame}[t,plain]{Unexpressed subjects}

\ex. John seems to win the race.

\ex. John hopes to win the race.

\pause
\vspace{10pt}
\ex. It seems that John wins the race.

\ex. *It hopes that John wins the race.


\end{frame}

\begin{frame}[t,plain]{Unexpressed subjects}

\vspace{50pt}
\hspace{60pt}John\hspace{20pt} seems\hspace{20pt} to\hspace{20pt} win\hspace{20pt} the\hspace{20pt} race.
\vspace{50pt}

\hspace{60pt}John\hspace{20pt} hopes\hspace{20pt} PRO\hspace{20pt} to\hspace{20pt} win\hspace{20pt} the\hspace{20pt} race.


\end{frame}
\begin{frame}[t,plain]{}

\end{frame}
\begin{frame}[t,plain]{}

\end{frame}
\begin{frame}[t,plain]{}

\end{frame}
\begin{frame}[t,plain]{}

\end{frame}
\end{document}
