\documentclass[ignorenonframetext,8pt,aspectratio=169]{beamer}

\usepackage{umut}
\usepackage{umuttr}
\usepackage{usynsem}
\usepackage[utf8]{inputenc}
\usepackage{uling}
\usepackage{natbib,unatbib}
\usepackage{linguex}
         \renewcommand{\refdash}{}
\usepackage{ubeamer}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{fancyvrb}

\usepackage{tikz-qtree}
\usetikzlibrary{er,positioning}

\title{Movement as Remerge}
\author{\  \\  {\it Partly based on Koeneman \& Zeiljstra (2017)} \\ \vspace{20pt} Umut \"Ozge\\  }

\date{COGS 532: Theoretical Linguistics\\ METU, Informatics}

\begin{document}

\begin{frame}\frametitle{}
\thispagestyle{empty}
\maketitle
\end{frame}

\begin{frame}[t,plain]{Movement/Displacement}

		\ex. \a. Adrian has always liked this yellow chair.
		\b. Which chair has Adrian always liked?
		\b. Which chair has Adrian always liked <this yellow chair>?

\bigskip

		\ex.\a. John saw the man with the telescope.
		\b. Which telescope did John see the man with?
		\b. Which telescope did John see the man with <the telescope>?

\bigskip

\ex. \a. I think Mary posted some pictures of herself.
\b. Which pictures of herself do you think Mary posted?
\b. Which pictures of herself do you think Mary posted <some pictures of herself>?

\end{frame}

\begin{frame}[t,plain]{Unbounded dependencies} 

		\ex. \a. Adrian has always liked this yellow chair.
		\b. Which yellow chair has Adrian always liked?
		\b. Which yellow chair did you say that Adrian has always liked?
		\b. Which yellow chair do you think that I said that Adrian has always liked?

\end{frame}

\begin{frame}[t,plain]{Remerge}

		\ex. 
		\a. You think that I said that Adrian has always liked this yellow chair.
		\b.  Which yellow chair do you think that I said that Adrian has always liked?
		\b.  Which yellow chair do you think that I said that Adrian has always liked <this yellow chair>?
		\b. Which yellow chair is such that you think that I said that Adrian has always liked this yellow chair?

\end{frame}

\begin{frame}[t,plain]{Structure building and Remerge}
\bigskip
\bigskip
		\begin{center}
		\Tree [.WP W XP ] 
		\hspace{20pt}
		\Tree [.YP Y [.WP W XP ] ]
		\hspace{20pt}
		\Tree [.ZP Z [.YP Y [.WP W XP ] ] ]
		\Tree [.YP \alert{XP} [.Y' Y [.WP W \alert{<XP>} ] ] ]
		\end{center}


\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\begin{frame}[t,plain]{}

\end{frame}

\end{document}

